waRne - Putting cricket analytics in a spin

### 2020-10-01 James_paper_copy.Rmd
update on the dhoni dilema

---
title: "waRne - Putting cricket analytics in a spin"
bibliography: references.bib
output:
  pdf_document:
    toc: yes
  html_document:
    keep_md: yes
    toc: yes
    toc_float: yes
authors: Robert(1), James (2)
---

@@

bowler_vars <- 
  player_database %>% 
  dplyr::select(-c(batting_style, player_name)) %>% 
  drop_na()%>% 
  mutate(bowling_style = recode(bowling_style, "Right-arm fast" = "Pace",
                                "Slow left-arm orthodox"= "Spin",
                                "Legbreak"= "Spin",
                                "Right-arm medium"= "Pace",
                                "Left-arm medium-fast"= "Pace",
                                "Right-arm offbreak"= "Spin",
                                "Legbreak googly"= "Spin",
                                "Left-arm fast"= "Pace",
                                "Right-arm medium-fast"= "Pace",
                                "Left-arm fast-medium"= "Pace",
                                "Right-arm fast-medium"= "Pace",
                                "Left-arm medium"= "Pace",
                                "Slow left-arm chinaman"= "Spin",
                                "Right-arm offbreak, Legbreak"= "Spin",
                                "Right-arm medium, Right-arm offbreak"= "Spin",
                                "Left-arm medium, Slow left-arm orthodox, 
                                               Slow left-arm chinaman"= "Spin", 
                                "Left-arm medium, Slow left-arm orthodox, Slow left-arm chinaman" = "Spin"))

@@

1-pnorm(abs(z))

@@

With this new dataset, we allow fans to put on their analyst thats and to be able to ask themselves, what exactly makes a good closer and what exactly is the Dhoni Dilemma.

To understand the Dhoni Deilemma, we need to see some interesting things to do with the change in RRR.

Cricket is an obvious sort of sport, to win in the end you have to get one run more than your opposition. A commonly used statistic during the broadcast is the required run rate, for example if you need 120 to win off 20 overs your RRR is \$6\$ runs an over

What follows is then obvious is the chasing team wins if they are able to lower the RRR that is score quicker.

@@

```{r}
# graph of powerplay
```

This graph makes sense as we can see the best openers in the world lower the required run rate so whats the Dhoni Dilemma?

```{r}
# middle overs (enter in the middle)
```

Dhoni is renowed for being one of the worlds best closers but we can see it seems as though in the middle he is letting the game get out of hand. How can one of the worlds best closers

>>>>

---
title: "waRne - Putting cricket analytics in a spin"
bibliography: references.bib
output:
  html_document:
    keep_md: yes
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
authors: Robert(1), James (2)
---

@@

bowler_vars <- 
  player_database %>% 
  dplyr::select(-c(batting_style, player_name)) %>% 
  drop_na()%>% 
  mutate(pace_spin = bowling_style, "Right-arm fast" = "Pace",
                                "Slow left-arm orthodox"= "Spin",
                                "Legbreak"= "Spin",
                                "Right-arm medium"= "Pace",
                                "Left-arm medium-fast"= "Pace",
                                "Right-arm offbreak"= "Spin",
                                "Legbreak googly"= "Spin",
                                "Left-arm fast"= "Pace",
                                "Right-arm medium-fast"= "Pace",
                                "Left-arm fast-medium"= "Pace",
                                "Right-arm fast-medium"= "Pace",
                                "Left-arm medium"= "Pace",
                                "Slow left-arm chinaman"= "Spin",
                                "Right-arm offbreak, Legbreak"= "Spin",
                                "Right-arm medium, Right-arm offbreak"= "Spin",
                                "Left-arm medium, Slow left-arm orthodox, 
                                               Slow left-arm chinaman"= "Spin", 
                                "Left-arm medium, Slow left-arm orthodox, Slow left-arm chinaman" = "Spin")

@@

2*(pnorm(z))

@@

With this new dataset, we allow fans to put on their analyst thats and to be able to ask themselves, what exactly makes a good closer and what exactly is the Dhoni Dilemma. To understand the Dhoni Deilemma, we need to see some interesting things to do with the change in RRR.

Cricket is an obvious sort of sport, to win in the end you have to get one run more than your opposition. A commonly used statistic during the broadcast is the required run rate, for example if you need 120 to win off 20 overs your RRR is \$6\$ runs an over. What follows is then obvious is the chasing team wins if they are able to lower the RRR that is score quicker.

@@

```{r}
# graph of powerplay

opening_batsman_of_interest <- c(
  # 230559, #pollard
  48472, #t dilshaan
  37737, #brendon mccalum
  8180, #shane watson
  47270, #greme smith, 
  28763, #gautham gambhir
  226492, #martn guptil
  49289, #mahela jayawardene
  56194, #tamim iqbal
  55608, #hamilton masakadza
  51880, #gayle
  41434, #mohommad hafeez
  259410, #ahmed shehzad
  24611, #william porterfield
  # 49209, #sanath jayasuriya
  43906, #hashim amla
  16406, #michael lumb
  # 42683, #salman butt
  # 325012, #stoinis
  # 272450, #MR Marsh
  # 28081, #Dhoni
  # 253802, #kholi
  5334, #finch
  219889, #warner
  # 326434, #carey
  267192, #smith
  # 505120, #agar
  # 530011, #head
  # 5961, #henriques
  # 325026, #maxwell
  # 25913, #nabu
  # 4864, #christian,
  # 270484, #faulkner
  # 230193, #wade
  # 233680, #wells
  # 500268, #turner
  # 334337, #handscomb
  # 603410, #mcdermott
  # 308798  #short
  # 787987, #labuschagne
  # 1124282, # josh phillipe
  # 326637, #Chris Lyrnn
  # 5939, #hussey
  # 931581 #pant
  308967, # jos buttler
  253802, #Kohli
  249866  # alex hales
)

# Dot plot for openers
cricjam_data_big %>% 
  dplyr::filter(inning == 2, 
                batsman_id %in% opening_batsman_of_interest, 
                # batsman_balls_faced_this_match<16, 
                !is.infinite(required_run_rate), 
                over<6) %>% 
  group_by(batsman_name) %>% 
  summarise(change = mean(change_in_requireed_run_rate), 
            total_balls_faced = n()) %>% 
  ggplot(aes(x = total_balls_faced, y = change, label = batsman_name)) +
  geom_point(size = 2) +
  xlim(c(50, 1250))+
  geom_text(vjust = 1.4, color = "black") +
  theme_minimal()+
  labs(x = "Balls Faced", 
       y = "Average Change in Required Run Rate", 
       title = "Top Opening Batsmen T20")
  theme(axis.text = element_text(size = 12), 
        axis.title = element_text(size = 16),
        plot.title = element_text(size = 16))

This graph makes sense as we can see some of the best openers in the world lower the required run rate. So what is the Dhoni Dilemma?

Dhoni is considered the greatest closing batsman in the world. He has pulled of many spectacular saves, and has T20 and T20I strike rates after 14 years in the game. But how does his required run rate compare to other middle order and closing batsman

```{r}
# middle overs (enter in the middle)

middle_batsman_of_interest <- c(
  230559, #pollard
  32498, #yusef pathan
  321777, #david miller
  44936, #AB De Villiers
  276298, #andre russell
  8180, #shane watson
  34102, #rohit sharma
  # 51880, #gayle
  # 325012, #stoinis
  # 272450, #MR Marsh
  28081, #Dhoni
  # 253802, #kholi
  # 5334, #finch
  # 219889, #warner
  # 326434, #carey
  # 267192, #smith
  # 505120, #agar
  # 530011, #head
  # 5961, #henriques
  325026 #maxwell
  # 25913, #nabu
  # 4864, #christian,
  # 270484, #faulkner
  # 230193, #wade
  # 233680, #wells
  # 500268, #turner
  # 334337, #handscomb
  # 603410, #mcdermott
  # 308798  #short
  # 787987, #labuschagne
  # 1124282, # josh phillipe
  # 326637, #Chris Lyrnn
  # 5939, #hussey
  # 931581 #pant
  # 308967, # job buttler
  # 249866  # alex hales
)

cricjam_data_big %>% 
  dplyr::filter(inning == 2, 
                batsman_id %in% middle_batsman_of_interest, 
                # batsman_balls_faced_this_match<16, 
                !is.infinite(required_run_rate), 
                # min(batsman_balls_faced_this_match)==1,
                over<16, 
                over>=6) %>% 
  group_by(batsman_id, match_id) %>% 
  mutate(min_balls = if_else(min(batsman_balls_faced_this_match)==1, 1, 0)) %>% 
  ungroup() %>% 
  # dplyr::filter(min_balls==1) %>%
  group_by(batsman_name) %>% 
	# dplyr::filter(batsman_id == 28081) %>% ggplot(aes(x = change_in_requireed_run_rate))+geom_histogram()
  summarise(change = mean(change_in_requireed_run_rate), 
            total_balls_faced = n()) %>% 
  ggplot(aes(x = total_balls_faced, y = change, label = batsman_name)) +
  geom_point() +
	xlim(c(300, 1300))+
  # geom_text(vjust = 1, color = "black") +
  labs(x = "Balls Faced", 
       y = "Average Change in Required Run Rate", 
       title = "Top Middle Batsmen T20")+
  geom_text(vjust = 1.4, color = "black") +
  theme_minimal() 
  theme(axis.text = element_text(size = 12), 
        axis.title = element_text(size = 16),
        plot.title = element_text(size = 16))

Dhoni is renowed for being one of the worlds best closers but we can see it seems as though in the middle he is letting the game get out of hand. How can one of the worlds best closers let the run rate go up so consistently in the middle overs?

One possible explanation comes from looking at the acceleration of Dhoni compared to these other middle order batsmen. Dhoni comes in usually around overs 11/12, and from the plot below we can see that he is a slow starter, it takes several overs for him to get his strike rate up, which consistently stays high throughout the game even when other batsmen's begins to drop off.

cricjam_data_big %>%
	dplyr::filter(batsman_id == 28081, 
								batsman_balls_faced_this_match == 1) %>%
	group_by(bucketed_over) %>% 
	summarise(total = n()) %>% 
	ungroup() %>% 
	mutate(mean(total))

cricjam_data_big %>% 
    dplyr::filter(batsman_id %in% middle_batsman_of_interest, 
                  !is.infinite(required_run_rate), 
                  over>=6, 
    							# over <16
                  # batsman_id == 5961
                  # batsman_balls_faced_this_match == 1
                  ) %>% 
    # dplyr::select(over, earned_runs, play_description) %>%
    # group_by(earned_runs) %>% 
    # summarise(n())
    # group_by(batsman_id, match_id) %>% 
    # mutate(min_balls = if_else(min(batsman_balls_faced_this_match)==1, 1, 0)) %>% 
    # ungroup() %>%
    group_by(batsman_balls_faced_this_match, batsman_name) %>%  # from here to the next comment is for sr, the rest is for 
    summarise(sr = 100*sum(extra_runs+earned_runs)/n(), 
              count = n()) %>% 
    # dplyr::filter(batsman_balls_faced_this_match<50) %>% 
    ggplot(aes(x = batsman_balls_faced_this_match, y = sr)) + 
    geom_smooth() +
    geom_hline(yintercept = 120) +
    ylim(c(0,200))+
    labs(x = "Balls Faced", 
         y = "Strike Rate", 
         title = "Batsman Acceleration In Overs 11-20")+
    theme_minimal() +
    theme(axis.text = element_text(size = 12), 
          axis.title = element_text(size = 16),
          plot.title = element_text(size = 16)) +
    # ylim(c(50, 200))+
    facet_wrap(~batsman_name)

Another is the effort of Dhoni's partners in moving the game along while Dhoni is up

middle_batsman_of_interest <- c(
  230559, #pollard
  32498, #yusef pathan
  321777, #david miller
  44936, #AB De Villiers
  276298, #andre russell
  8180, #shane watson
  34102, #rohit sharma
  28081, #Dhoni
  325026 #maxwell
  )  
maxwell <-
  cricjam_data_big %>% 
  dplyr::filter(batsman_id %in% 325026, 
                inning == 2, resources>10,
                # batsman_balls_faced_this_match<16, 
                !is.infinite(required_run_rate), 
                over < 16,
                over >= 6 
                # batsman_balls_faced_this_match==1, 
                # year %in% c("2017", "2018", "2019", "20172018", "20182019", "2020", "20192020")
  ) %>% 
  distinct(match_id, bucketed_over) %>% 
  left_join(cricjam_data_big %>% 
              dplyr::filter(inning == 2, 
                            !is.infinite(required_run_rate), 
                            over < 16,
              							resources>10,
                            over >= 6), by = c("match_id" = "match_id", 
                                               "bucketed_over" = "bucketed_over")) %>% 
  group_by(bucketed_over, match_id) %>% 
  mutate(starting_rrr = first(required_run_rate), 
         ending_rrr = last(required_run_rate), 
         diff = ending_rrr-starting_rrr) %>% 
  group_by(bucketed_over) %>% 
  summarise(avg_Maxwell = mean(diff))  %>% 
	mutate(batsman_partner_Maxwell = "Partnership") %>% 
	bind_rows(cricjam_data_big %>% 
							dplyr::filter(batsman_id %in% 325026, 
                inning == 2, 
                # batsman_balls_faced_this_match<16, 
                !is.infinite(required_run_rate), 
                over < 16,resources>10,
                over >= 6 
                # batsman_balls_faced_this_match==1, 
                # year %in% c("2017", "2018", "2019", "20172018", "20182019", "2020", "20192020")
  ) %>% 
  distinct(match_id, bucketed_over) %>% 
  left_join(cricjam_data_big %>% 
              dplyr::filter(inning == 2, 
                            !is.infinite(required_run_rate), 
                            over < 16,
              							resources>10,
                            over >= 6), by = c("match_id" = "match_id", 
                                               "bucketed_over" = "bucketed_over")) %>% 
  group_by(bucketed_over, match_id) %>% 
  mutate(starting_rrr = first(required_run_rate), 
         ending_rrr = last(required_run_rate), 
         diff = ending_rrr-starting_rrr, 
  			 batsman_partner_Maxwell = if_else(batsman_id == 325026, "Batsman", "Partner")) %>% 
  group_by(bucketed_over, batsman_partner_Maxwell) %>% 
  summarise(avg_Maxwell = mean(diff)) %>% 
  ungroup()) %>% 
	mutate(batsman_name = "Maxwell", 
				 avg = avg_Maxwell, 
				 batsman_partner = batsman_partner_Maxwell) %>% 
	dplyr::select(c(batsman_name, avg, batsman_partner, bucketed_over))

dhoni <-
  cricjam_data_big %>% 
  dplyr::filter(batsman_id %in% 28081, 
                inning == 2, 
  							resources>10,
                # batsman_balls_faced_this_match<16, 
                !is.infinite(required_run_rate), 
                over < 16,
                over >= 6 
                # batsman_balls_faced_this_match==1, 
                # year %in% c("2017", "2018", "2019", "20172018", "20182019", "2020", "20192020")
  ) %>% 
  distinct(match_id, bucketed_over) %>% 
  left_join(cricjam_data_big %>% 
              dplyr::filter(inning == 2, 
                            !is.infinite(required_run_rate), 
                            over < 16,
              							resources>10,
                            over >= 6), by = c("match_id" = "match_id", 
                                               "bucketed_over" = "bucketed_over")) %>% 
  group_by(bucketed_over, match_id) %>% 
  mutate(starting_rrr = first(required_run_rate), 
         ending_rrr = last(required_run_rate), 
         diff = ending_rrr-starting_rrr) %>% 
  group_by(bucketed_over) %>% 
  summarise(avg_Dhoni = mean(diff)) %>% 
	mutate(batsman_partner_Dhoni = "Partnership") %>% 
	bind_rows(cricjam_data_big %>% 
							dplyr::filter(batsman_id %in% 28081, 
                inning == 2, 
                # batsman_balls_faced_this_match<16, 
                !is.infinite(required_run_rate), 
                over < 16,
														resources>10,
                over >= 6 
                # batsman_balls_faced_this_match==1, 
                # year %in% c("2017", "2018", "2019", "20172018", "20182019", "2020", "20192020")
  ) %>% 
  distinct(match_id, bucketed_over) %>% 
  left_join(cricjam_data_big %>% 
              dplyr::filter(inning == 2, 
                            !is.infinite(required_run_rate), 
                            over < 16,
              							resources>10,
                            over >= 6), by = c("match_id" = "match_id", 
                                               "bucketed_over" = "bucketed_over")) %>% 
  group_by(bucketed_over, match_id) %>% 
  mutate(starting_rrr = first(required_run_rate), 
         ending_rrr = last(required_run_rate), 
         diff = ending_rrr-starting_rrr, 
  			 batsman_partner_Dhoni = if_else(batsman_id == 28081, "Batsman", "Partner")) %>% 
  group_by(bucketed_over, batsman_partner_Dhoni) %>% 
  summarise(avg_Dhoni = mean(diff)) %>% 
  ungroup()) %>% 
	mutate(batsman_name = "Dhoni", 
				 avg = avg_Dhoni, 
				 batsman_partner = batsman_partner_Dhoni) %>% 
	dplyr::select(c(batsman_name, avg, batsman_partner, bucketed_over))

# sharma <-
#   cricjam_data_big %>% 
#   dplyr::filter(batsman_id %in% 34102, 
#                 inning == 2, 
#                 # batsman_balls_faced_this_match<16, 
#                 !is.infinite(required_run_rate), 
#                 over < 16,
#                 over >= 6 
#                 # batsman_balls_faced_this_match==1, 
#                 # year %in% c("2017", "2018", "2019", "20172018", "20182019", "2020", "20192020")
#   ) %>% 
#   distinct(match_id, bucketed_over) %>% 
#   left_join(cricjam_data_big %>% 
#               dplyr::filter(inning == 2, 
#                             !is.infinite(required_run_rate), 
#                             over < 16,
#                             over >= 6), by = c("match_id" = "match_id", 
#                                                "bucketed_over" = "bucketed_over")) %>% 
#   group_by(bucketed_over, match_id) %>% 
#   mutate(starting_rrr = first(required_run_rate), 
#          ending_rrr = last(required_run_rate), 
#          diff = ending_rrr-starting_rrr) %>% 
#   group_by(bucketed_over) %>% 
#   summarise(avg_Sharma = mean(diff)) %>% 
# 	mutate(batsman_partner_Sharma = "Partnership") %>% 
# 	bind_rows(cricjam_data_big %>% 
# 							dplyr::filter(batsman_id %in% 34102, 
#                 inning == 2, 
#                 # batsman_balls_faced_this_match<16, 
#                 !is.infinite(required_run_rate), 
#                 over < 16,
#                 over >= 6 
#                 # batsman_balls_faced_this_match==1, 
#                 # year %in% c("2017", "2018", "2019", "20172018", "20182019", "2020", "20192020")
#   ) %>% 
#   distinct(match_id, bucketed_over) %>% 
#   left_join(cricjam_data_big %>% 
#               dplyr::filter(inning == 2, 
#                             !is.infinite(required_run_rate), 
#                             over < 16,
#                             over >= 6), by = c("match_id" = "match_id", 
#                                                "bucketed_over" = "bucketed_over")) %>% 
#   group_by(bucketed_over, match_id) %>% 
#   mutate(starting_rrr = first(required_run_rate), 
#          ending_rrr = last(required_run_rate), 
#          diff = ending_rrr-starting_rrr, 
#   			 batsman_partner_Sharma = if_else(batsman_id == 34102, "Batsman", "Partner")) %>% 
#   group_by(bucketed_over, batsman_partner_Sharma) %>% 
#   summarise(avg_Sharma = mean(diff)) %>% 
#   ungroup()) %>% 
# 	mutate(batsman_name = "Sharma", 
# 				 avg = avg_Sharma, 
# 				 batsman_partner = batsman_partner_Sharma) %>% 
# 	dplyr::select(c(batsman_name, avg, batsman_partner, bucketed_over))

# watson <-
#   cricjam_data_big %>% 
#   dplyr::filter(batsman_id %in% 8180, 
#                 inning == 2, 
#                 # batsman_balls_faced_this_match<16, 
#                 !is.infinite(required_run_rate), 
#                 over < 16,
#                 over >= 6 
#                 # batsman_balls_faced_this_match==1, 
#                 # year %in% c("2017", "2018", "2019", "20172018", "20182019", "2020", "20192020")
#   ) %>% 
#   distinct(match_id, bucketed_over) %>% 
#   left_join(cricjam_data_big %>% 
#               dplyr::filter(inning == 2, 
#                             !is.infinite(required_run_rate), 
#                             over < 16,
#                             over >= 6), by = c("match_id" = "match_id", 
#                                                "bucketed_over" = "bucketed_over")) %>% 
#   group_by(bucketed_over, match_id) %>% 
#   mutate(starting_rrr = first(required_run_rate), 
#          ending_rrr = last(required_run_rate), 
#          diff = ending_rrr-starting_rrr) %>% 
#   group_by(bucketed_over) %>% 
#   summarise(avg_Watson = mean(diff)) %>% 
# 	mutate(batsman_partner_Watson = "Partnership") %>% 
# 	bind_rows(cricjam_data_big %>% 
# 							dplyr::filter(batsman_id %in% 8180, 
#                 inning == 2, 
#                 # batsman_balls_faced_this_match<16, 
#                 !is.infinite(required_run_rate), 
#                 over < 16,
#                 over >= 6 
#                 # batsman_balls_faced_this_match==1, 
#                 # year %in% c("2017", "2018", "2019", "20172018", "20182019", "2020", "20192020")
#   ) %>% 
#   distinct(match_id, bucketed_over) %>% 
#   left_join(cricjam_data_big %>% 
#               dplyr::filter(inning == 2, 
#                             !is.infinite(required_run_rate), 
#                             over < 16,
#                             over >= 6), by = c("match_id" = "match_id", 
#                                                "bucketed_over" = "bucketed_over")) %>% 
#   group_by(bucketed_over, match_id) %>% 
#   mutate(starting_rrr = first(required_run_rate), 
#          ending_rrr = last(required_run_rate), 
#          diff = ending_rrr-starting_rrr, 
#   			 batsman_partner_Watson = if_else(batsman_id == 8180, "Batsman", "Partner")) %>% 
#   group_by(bucketed_over, batsman_partner_Watson) %>% 
#   summarise(avg_Watson = mean(diff)) %>% 
#   ungroup()) %>% 
# 	mutate(batsman_name = "Watson", 
# 				 avg = avg_Watson, 
# 				 batsman_partner = batsman_partner_Watson) %>% 
# 	dplyr::select(c(batsman_name, avg, batsman_partner, bucketed_over))

russell <-
  cricjam_data_big %>% 
  dplyr::filter(batsman_id %in% 276298, 
                inning == 2, 
                # batsman_balls_faced_this_match<16, 
                !is.infinite(required_run_rate), 
                over < 16,
  							resources>10,
                over >= 6 
                # batsman_balls_faced_this_match==1, 
                # year %in% c("2017", "2018", "2019", "20172018", "20182019", "2020", "20192020")
  ) %>% 
  distinct(match_id, bucketed_over) %>% 
  left_join(cricjam_data_big %>% 
              dplyr::filter(inning == 2, 
                            !is.infinite(required_run_rate), 
                            over < 16,
              							resources>10,
                            over >= 6), by = c("match_id" = "match_id", 
                                               "bucketed_over" = "bucketed_over")) %>% 
  group_by(bucketed_over, match_id) %>% 
  mutate(starting_rrr = first(required_run_rate), 
         ending_rrr = last(required_run_rate), 
         diff = ending_rrr-starting_rrr) %>% 
  group_by(bucketed_over) %>% 
  summarise(avg_Russell = mean(diff)) %>% 
	mutate(batsman_partner_Russell = "Partnership") %>% 
	bind_rows(cricjam_data_big %>% 
							dplyr::filter(batsman_id %in% 276298, 
                inning == 2, 
                # batsman_balls_faced_this_match<16, 
                !is.infinite(required_run_rate), 
                over < 16,
														resources>10,
                over >= 6 
                # batsman_balls_faced_this_match==1, 
                # year %in% c("2017", "2018", "2019", "20172018", "20182019", "2020", "20192020")
  ) %>% 
  distinct(match_id, bucketed_over) %>% 
  left_join(cricjam_data_big %>% 
              dplyr::filter(inning == 2, 
                            !is.infinite(required_run_rate), 
                            over < 16,
              							resources>10,
                            over >= 6), by = c("match_id" = "match_id", 
                                               "bucketed_over" = "bucketed_over")) %>% 
  group_by(bucketed_over, match_id) %>% 
  mutate(starting_rrr = first(required_run_rate), 
         ending_rrr = last(required_run_rate), 
         diff = ending_rrr-starting_rrr, 
  			 batsman_partner_Russell = if_else(batsman_id == 276298, "Batsman", "Partner")) %>% 
  group_by(bucketed_over, batsman_partner_Russell) %>% 
  summarise(avg_Russell = mean(diff)) %>% 
  ungroup()) %>% 
	mutate(batsman_name = "Russell", 
				 avg = avg_Russell, 
				 batsman_partner = batsman_partner_Russell) %>% 
	dplyr::select(c(batsman_name, avg, batsman_partner, bucketed_over))

# villiers <-
#   cricjam_data_big %>% 
#   dplyr::filter(batsman_id %in% 44936, 
#                 inning == 2, 
#                 # batsman_balls_faced_this_match<16, 
#                 !is.infinite(required_run_rate), 
#                 over < 16,
#                 over >= 6 
#                 # batsman_balls_faced_this_match==1, 
#                 # year %in% c("2017", "2018", "2019", "20172018", "20182019", "2020", "20192020")
#   ) %>% 
#   distinct(match_id, bucketed_over) %>% 
#   left_join(cricjam_data_big %>% 
#               dplyr::filter(inning == 2, 
#                             !is.infinite(required_run_rate), 
#                             over < 16,
#                             over >= 6), by = c("match_id" = "match_id", 
#                                                "bucketed_over" = "bucketed_over")) %>% 
#   group_by(bucketed_over, match_id) %>% 
#   mutate(starting_rrr = first(required_run_rate), 
#          ending_rrr = last(required_run_rate), 
#          diff = ending_rrr-starting_rrr) %>% 
#   group_by(bucketed_over) %>% 
#   summarise(avg_DeVilliers = mean(diff)) %>% 
# 	mutate(batsman_partner_DeVilliers = "Partnership") %>% 
# 	bind_rows(cricjam_data_big %>% 
# 							dplyr::filter(batsman_id %in% 44936, 
#                 inning == 2, 
#                 # batsman_balls_faced_this_match<16, 
#                 !is.infinite(required_run_rate), 
#                 over < 16,
#                 over >= 6 
#                 # batsman_balls_faced_this_match==1, 
#                 # year %in% c("2017", "2018", "2019", "20172018", "20182019", "2020", "20192020")
#   ) %>% 
#   distinct(match_id, bucketed_over) %>% 
#   left_join(cricjam_data_big %>% 
#               dplyr::filter(inning == 2, 
#                             !is.infinite(required_run_rate), 
#                             over < 16,
#                             over >= 6), by = c("match_id" = "match_id", 
#                                                "bucketed_over" = "bucketed_over")) %>% 
#   group_by(bucketed_over, match_id) %>% 
#   mutate(starting_rrr = first(required_run_rate), 
#          ending_rrr = last(required_run_rate), 
#          diff = ending_rrr-starting_rrr, 
#   			 batsman_partner_DeVilliers = if_else(batsman_id == 44936, "Batsman", "Partner")) %>% 
#   group_by(bucketed_over, batsman_partner_DeVilliers) %>% 
#   summarise(avg_DeVilliers = mean(diff)) %>% 
#   ungroup()) %>% 
# 	mutate(batsman_name = "DeVilliers", 
# 				 avg = avg_DeVilliers, 
# 				 batsman_partner = batsman_partner_DeVilliers) %>% 
# 	dplyr::select(c(batsman_name, avg, batsman_partner, bucketed_over))

# miller <-
#   cricjam_data_big %>% 
#   dplyr::filter(batsman_id %in% 321777, 
#                 inning == 2, 
#                 # batsman_balls_faced_this_match<16, 
#                 !is.infinite(required_run_rate), 
#                 over < 16,
#                 over >= 6 
#                 # batsman_balls_faced_this_match==1, 
#                 # year %in% c("2017", "2018", "2019", "20172018", "20182019", "2020", "20192020")
#   ) %>% 
#   distinct(match_id, bucketed_over) %>% 
#   left_join(cricjam_data_big %>% 
#               dplyr::filter(inning == 2, 
#                             !is.infinite(required_run_rate), 
#                             over < 16,
#                             over >= 6), by = c("match_id" = "match_id", 
#                                                "bucketed_over" = "bucketed_over")) %>% 
#   group_by(bucketed_over, match_id) %>% 
#   mutate(starting_rrr = first(required_run_rate), 
#          ending_rrr = last(required_run_rate), 
#          diff = ending_rrr-starting_rrr) %>% 
#   group_by(bucketed_over) %>% 
#   summarise(avg_Miller = mean(diff)) %>% 
# 	mutate(batsman_partner_Miller = "Partnership") %>% 
# 	bind_rows(cricjam_data_big %>% 
# 							dplyr::filter(batsman_id %in% 321777, 
#                 inning == 2, 
#                 # batsman_balls_faced_this_match<16, 
#                 !is.infinite(required_run_rate), 
#                 over < 16,
#                 over >= 6 
#                 # batsman_balls_faced_this_match==1, 
#                 # year %in% c("2017", "2018", "2019", "20172018", "20182019", "2020", "20192020")
#   ) %>% 
#   distinct(match_id, bucketed_over) %>% 
#   left_join(cricjam_data_big %>% 
#               dplyr::filter(inning == 2, 
#                             !is.infinite(required_run_rate), 
#                             over < 16,
#                             over >= 6), by = c("match_id" = "match_id", 
#                                                "bucketed_over" = "bucketed_over")) %>% 
#   group_by(bucketed_over, match_id) %>% 
#   mutate(starting_rrr = first(required_run_rate), 
#          ending_rrr = last(required_run_rate), 
#          diff = ending_rrr-starting_rrr, 
#   			 batsman_partner_Miller = if_else(batsman_id == 321777, "Batsman", "Partner")) %>% 
#   group_by(bucketed_over, batsman_partner_Miller) %>% 
#   summarise(avg_Miller = mean(diff)) %>% 
#   ungroup()) %>% 
# 	mutate(batsman_name = "Miller", 
# 				 avg = avg_Miller, 
# 				 batsman_partner = batsman_partner_Miller) %>% 
# 	dplyr::select(c(batsman_name, avg, batsman_partner, bucketed_over))

# pathan <-
#   cricjam_data_big %>% 
#   dplyr::filter(batsman_id %in% 32498, 
#                 inning == 2, 
#                 # batsman_balls_faced_this_match<16, 
#                 !is.infinite(required_run_rate), 
#                 over < 16,
#                 over >= 6 
#                 # batsman_balls_faced_this_match==1, 
#                 # year %in% c("2017", "2018", "2019", "20172018", "20182019", "2020", "20192020")
#   ) %>% 
#   distinct(match_id, bucketed_over) %>% 
#   left_join(cricjam_data_big %>% 
#               dplyr::filter(inning == 2, 
#                             !is.infinite(required_run_rate), 
#                             over < 16,
#                             over >= 6), by = c("match_id" = "match_id", 
#                                                "bucketed_over" = "bucketed_over")) %>% 
#   group_by(bucketed_over, match_id) %>% 
#   mutate(starting_rrr = first(required_run_rate), 
#          ending_rrr = last(required_run_rate), 
#          diff = ending_rrr-starting_rrr) %>% 
#   group_by(bucketed_over) %>% 
#   summarise(avg_Pathan = mean(diff)) %>% 
# 	mutate(batsman_partner_Pathan = "Partnership") %>% 
# 	bind_rows(cricjam_data_big %>% 
# 							dplyr::filter(batsman_id %in% 32498, 
#                 inning == 2, 
#                 # batsman_balls_faced_this_match<16, 
#                 !is.infinite(required_run_rate), 
#                 over < 16,
#                 over >= 6 
#                 # batsman_balls_faced_this_match==1, 
#                 # year %in% c("2017", "2018", "2019", "20172018", "20182019", "2020", "20192020")
#   ) %>% 
#   distinct(match_id, bucketed_over) %>% 
#   left_join(cricjam_data_big %>% 
#               dplyr::filter(inning == 2, 
#                             !is.infinite(required_run_rate), 
#                             over < 16,
#                             over >= 6), by = c("match_id" = "match_id", 
#                                                "bucketed_over" = "bucketed_over")) %>% 
#   group_by(bucketed_over, match_id) %>% 
#   mutate(starting_rrr = first(required_run_rate), 
#          ending_rrr = last(required_run_rate), 
#          diff = ending_rrr-starting_rrr, 
#   			 batsman_partner_Pathan = if_else(batsman_id == 32498, "Batsman", "Partner")) %>% 
#   group_by(bucketed_over, batsman_partner_Pathan) %>% 
#   summarise(avg_Pathan = mean(diff)) %>% 
#   ungroup())%>% 
# 	mutate(batsman_name = "Pathan", 
# 				 avg = avg_Pathan, 
# 				 batsman_partner = batsman_partner_Pathan) %>% 
# 	dplyr::select(c(batsman_name, avg, batsman_partner, bucketed_over))

pollard <-
  cricjam_data_big %>% 
  dplyr::filter(batsman_id %in% 230559, 
                inning == 2, 
                # batsman_balls_faced_this_match<16, 
                !is.infinite(required_run_rate), 
                over < 16,
  							resources>10,
                over >= 6 
                # batsman_balls_faced_this_match==1, 
                # year %in% c("2017", "2018", "2019", "20172018", "20182019", "2020", "20192020")
  ) %>% 
  distinct(match_id, bucketed_over) %>% 
  left_join(cricjam_data_big %>% 
              dplyr::filter(inning == 2, 
                            !is.infinite(required_run_rate), 
                            over < 16,
              							resources>10,
                            over >= 6), by = c("match_id" = "match_id", 
                                               "bucketed_over" = "bucketed_over")) %>% 
  group_by(bucketed_over, match_id) %>% 
  mutate(starting_rrr = first(required_run_rate), 
         ending_rrr = last(required_run_rate), 
         diff = ending_rrr-starting_rrr) %>% 
  group_by(bucketed_over) %>% 
  summarise(avg_Pollard = mean(diff)) %>% 
	mutate(batsman_partner_Pollard = "Partnership") %>% 
	bind_rows(cricjam_data_big %>% 
							dplyr::filter(batsman_id %in% 230559, 
                inning == 2, 
                # batsman_balls_faced_this_match<16, 
                !is.infinite(required_run_rate), 
                over < 16,
														resources>10,
                over >= 6 
                # batsman_balls_faced_this_match==1, 
                # year %in% c("2017", "2018", "2019", "20172018", "20182019", "2020", "20192020")
  ) %>% 
  distinct(match_id, bucketed_over) %>% 
  left_join(cricjam_data_big %>% 
              dplyr::filter(inning == 2, 
                            !is.infinite(required_run_rate), 
                            over < 16,resources>10,
                            over >= 6), by = c("match_id" = "match_id", 
                                               "bucketed_over" = "bucketed_over")) %>% 
  group_by(bucketed_over, match_id) %>% 
  mutate(starting_rrr = first(required_run_rate), 
         ending_rrr = last(required_run_rate), 
         diff = ending_rrr-starting_rrr, 
  			 batsman_partner_Pollard = if_else(batsman_id == 230559, "Batsman", "Partner")) %>% 
  group_by(bucketed_over, batsman_partner_Pollard) %>% 
  summarise(avg_Pollard = mean(diff)) %>% 
  ungroup()) %>% 
	mutate(batsman_name = "Pollard", 
				 avg = avg_Pollard, 
				 batsman_partner = batsman_partner_Pollard) %>% 
	dplyr::select(c(batsman_name, avg, batsman_partner, bucketed_over))
